Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-14 analysis/paper/paper.Rmd
Use here to load files

load(
  system.file(
    "extdata",
    "m_f1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

load(
  system.file(
    "extdata",
    "m_g1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
```

>>>>

load(here("inst/extdata/m_f1.Rda"))
load(here("inst/extdata/m_f1_report.Rda"))
load(here("inst/extdata/m_f2.Rda"))
load(here("inst/extdata/m_f2_report.Rda"))

load(here("inst/extdata/m_g1.Rda"))
load(here("inst/extdata/m_g1_report.Rda"))

load(here("inst/extdata/m_g2.Rda"))
load(here("inst/extdata/m_g2_report.Rda"))

load(here("inst/extdata/m_h1.Rda"))
load(here("inst/extdata/m_h1_report.Rda"))
load(here("inst/extdata/m_h2.Rda"))
load(here("inst/extdata/m_h2_report.Rda"))
```
